\subsection{Applications of the BHH formula}
This research concerns the performance of formula \ref{eq:beardwood} for reasonable amounts of
locations $j$ a delivery person can visit in a workday, say $20\leq j\leq90$.
\citet{lei2015dynamic} estimates the values of $\beta$ for a selection of values for $j$.
In their research, the points were generated uniformly and the $L_2$ distance metric was used.
Table \ref{tab:beta-values} lists the results.
\begin{table}[H]
	\centering
	\caption{Empirical estimates of $\beta$ as a function of $j$, $20 \leq n \leq 90$ \citep{lei2015dynamic}}
	\label{tab:beta-values}
	\begin{tabular}{cc}
		\toprule
		$j$ & $\beta(j)$ \\
		\midrule
		20  & 0.8584265  \\
		30  & 0.8269698  \\
		40  & 0.8129900  \\
		50  & 0.7994125  \\
		60  & 0.7908632  \\
		70  & 0.7817751  \\
		80  & 0.7775367  \\
		90  & 0.7773827  \\
		\bottomrule
	\end{tabular}
\end{table}
\citet{figliozzi2008planning} is the first research to apply approximation formulas to real-world instances of TSPs (and VRPs (Vehicle Routing Problems)),
in the sense that distances between locations are measured over the actual road network.
An extension of formula \ref{eq:beardwood} that works for VRPs is assessed in this setting.
It is found that this model has an $R^2$ of 0.99 (which means 0.99 of the variation in TSP path length is explained by the formula) and MAPE
(Mean Absolute Prediction Error) of 4.2\%.
This prediction error is slightly higher than when it is applied to a setting where Euclidean distances are considered (3.0\%), but the formula still performs well
\citep{figliozzi2008planning}.

\citet{merchan2019empirical} use circuity factors to measure the relative detour incurred for traveling in a road network, compared to the Euclidean distance.
This circuity factor for locations $p$ and $q$ is defined as:
\begin{align}
	c = \frac{d_{c}(p,q)}{d_{L_{2}}(p,q)}
	\label{eq:circuity}
\end{align}
By definition, $c \geq 1$, as the Euclidean distance is the shortest possible path between two points in a plane.
Then, $\beta_c$ is estimated by $\beta_c=c\beta$. This value $c$, is estimated for three different areas in São Paulo, for which the results are listed in Table
\ref{tab:beta-merchan}.
These values indicate real travel distances are on average 2.76 times longer in area 1 compared to the $L_2$ metric.
These values were obtained by uniformly generating $n$ locations (for $n$ ranging from 3 to 250), computing near-optimal tour lengths under the Euclidean metric,
and solving for $\beta$, then scaling by the empirical circuity factor.
\begin{table}[H]
	\centering
	\caption{Estimates of the circuity factor $c$ and its corresponding $\beta_c$ \citep{merchan2019empirical}}
	\label{tab:beta-merchan}
	\begin{tabular}{lccc}
		\toprule
		          & Area 1 & Area 2 & Area 3 \\
		\midrule
		$c$       & 2.76   & 2.34   & 1.82   \\
		$\beta_c$ & 2.48   & 2.10   & 1.64   \\
		\bottomrule
	\end{tabular}
\end{table}
It is important to note, however, that the assumptions in this study may limit the generality of the findings.
In particular, the use of uniformly distributed locations does not accurately reflect the spatial distribution of delivery points in real urban environments,
where locations tend to cluster.
Within small urban areas, high-rise buildings and single-family homes may coexist in the same neighborhoods, challenging the assumption of uniformly distributed
delivery points.
